### 2018-02-07 inst/vign/taxize_vignette.Rmd
fixes to readme, and vignettes
updated vignettes

```{r}
out <- get_nbnid_("Poa annua")
NROW(out)
```

@@

```{r downstream1, eval=TRUE, cache=FALSE}
downstream("Apis", downto = "Species", db = "col")
```

@@

```{r downstream2, eval=TRUE, cache=FALSE}
downstream("Apis", downto = "Species", db = "itis")
```

@@

```{r}
children(get_colid("Apis"))
```

>>>>

```{r}
out <- get_nbnid_("Poa annua")
NROW(out$`Poa annua`)
```

@@

```{r downstream1, eval=TRUE, cache=FALSE}
apis_col_id <- "015be25f6b061ba517f495394b80f108" # id for Apis, fetched beforehand to save time here
downstream(apis_col_id, downto = "species", db = "col")
```

@@

```{r downstream2, eval=TRUE, cache=FALSE}
apis_itis_id <- 154395 # id for Apis, fetched beforehand to save time here
downstream(apis_itis_id, downto = "species", db = "itis")
```

@@

```{r}
# using the id for Apis we defined above for COL
children(apis_col_id, db = "col")
```
